\pkg{casebase}: An Alternative Framework For Survival Analysis and Comparison of Event Rates

### 2020-09-21 analysis/paper/paper.Rmd
equation references for CS1

For our first case study, we return to the ERSPC study and investigate the differences in risk between the control and screening arms. We fit four models that differ in which functional form of time is used: 1) excluded from the linear predictor, 2) linear function, 3) log function, and 4) a smooth function using cubic B-splines. The models are fit using \code{fitSmoothHazard} with the familiar formula interface:

>>>>

For our first case study, we return to the ERSPC study and investigate the differences in risk between the control and screening arms. We fit four models that differ in which functional form of time is used: 1) excluded from the linear predictor as seen in \eqref{eq:exp}, 2) linear function as seen in \eqref{eq:gomp}, 3) log function as seen in \eqref{eq:weibull}, and 4) a smooth function using cubic B-splines. The models are fit using \code{fitSmoothHazard} with the familiar formula interface:

### 2020-09-21 analysis/paper/paper.tex
equation references for CS1

This report was generated on 2020-09-20 20:42:38 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> R version 4.0.2 (2020-06-22)
#> Platform: x86_64-pc-linux-gnu (64-bit)
#> Running under: Pop!_OS 20.04 LTS
#> 
#> Matrix products: default
#> BLAS:   /usr/lib/x86_64-linux-gnu/openblas-pthread/libblas.so.3
#> LAPACK: /usr/lib/x86_64-linux-gnu/openblas-pthread/liblapack.so.3
#> 
#> locale:
#>  [1] LC_CTYPE=en_US.UTF-8       LC_NUMERIC=C              
#>  [3] LC_TIME=en_US.UTF-8        LC_COLLATE=en_US.UTF-8    
#>  [5] LC_MONETARY=en_US.UTF-8    LC_MESSAGES=en_US.UTF-8   
#>  [7] LC_PAPER=en_US.UTF-8       LC_NAME=C                 
#>  [9] LC_ADDRESS=C               LC_TELEPHONE=C            
#> [11] LC_MEASUREMENT=en_US.UTF-8 LC_IDENTIFICATION=C       
#> 
#> attached base packages:
#> [1] splines   stats     graphics  grDevices utils     datasets  methods  
#> [8] base     
#> 
#> other attached packages:
#>  [1] broom_0.7.0               dotwhisker_0.5.0         
#>  [3] timereg_1.9.7             glue_1.4.2               
#>  [5] scales_1.1.1              forcats_0.5.0            
#>  [7] stringr_1.4.0             dplyr_1.0.2              
#>  [9] purrr_0.3.4               readr_1.3.1              
#> [11] tidyr_1.1.2               ggplot2_3.3.2            
#> [13] tidyverse_1.3.0           lubridate_1.7.9          
#> [15] visreg_2.7.0              tibble_3.0.3             
#> [17] riskRegression_2020.02.05 prodlim_2019.11.13       
#> [19] flexsurv_1.1.1            survival_3.2-3           
#> [21] pracma_2.2.9              magrittr_1.5             
#> [23] kableExtra_1.2.1          glmnet_4.0-2             
#> [25] Matrix_1.2-18             data.table_1.13.0        
#> [27] cowplot_1.1.0             colorspace_1.4-1         
#> [29] casebase_0.9.0           
#> 
#> loaded via a namespace (and not attached):
#>  [1] TH.data_1.0-10      VGAM_1.1-3          ellipsis_0.3.1     
#>  [4] ggstance_0.3.4      htmlTable_2.1.0     base64enc_0.1-3    
#>  [7] fs_1.5.0            rstudioapi_0.11     farver_2.0.3       
#> [10] MatrixModels_0.4-1  fansi_0.4.1         mvtnorm_1.1-1      
#> [13] xml2_1.3.2          codetools_0.2-16    knitr_1.29         
#> [16] Formula_1.2-3       jsonlite_1.7.1      cluster_2.1.0      
#> [19] dbplyr_1.4.4        png_0.1-7           compiler_4.0.2     
#> [22] httr_1.4.2          backports_1.1.9     assertthat_0.2.1   
#> [25] cli_2.0.2           htmltools_0.5.0     quantreg_5.67      
#> [28] tools_4.0.2         gtable_0.3.0        Rcpp_1.0.5         
#> [31] cellranger_1.1.0    vctrs_0.3.4         nlme_3.1-149       
#> [34] conquer_1.0.2       iterators_1.0.12    xfun_0.17          
#> [37] rvest_0.3.6         lifecycle_0.2.0     polspline_1.1.19   
#> [40] muhaz_1.2.6.1       MASS_7.3-53         zoo_1.8-8          
#> [43] hms_0.5.3           sandwich_2.5-1      SparseM_1.78       
#> [46] RColorBrewer_1.1-2  rticles_0.15        yaml_2.2.1         
#> [49] gridExtra_2.3       rms_6.0-1           rpart_4.1-15       
#> [52] latticeExtra_0.6-29 stringi_1.5.3       highr_0.8          
#> [55] foreach_1.5.0       checkmate_2.0.0     lava_1.6.7         
#> [58] shape_1.4.5         rlang_0.4.7         pkgconfig_2.0.3    
#> [61] matrixStats_0.56.0  evaluate_0.14       lattice_0.20-41    
#> [64] labeling_0.3        htmlwidgets_1.5.1   cmprsk_2.2-10      
#> [67] tidyselect_1.1.0    deSolve_1.28        plyr_1.8.6         
#> [70] R6_2.4.1            generics_0.0.2      Hmisc_4.4-1        
#> [73] multcomp_1.4-13     DBI_1.1.0           withr_2.2.0        
#> [76] pillar_1.4.6        haven_2.3.1         foreign_0.8-79     
#> [79] mgcv_1.8-33         nnet_7.3-14         mstate_0.2.12      
#> [82] modelr_0.1.8        crayon_1.3.4        rmarkdown_2.3      
#> [85] jpeg_0.1-8.1        grid_4.0.2          readxl_1.3.1       
#> [88] blob_1.2.1          reprex_0.3.0        digest_0.6.25      
#> [91] webshot_0.5.2       numDeriv_2016.8-1.1 stats4_4.0.2       
#> [94] munsell_0.5.0       viridisLite_0.3.0   quadprog_1.5-8
\end{CodeOutput}
\end{CodeChunk}

>>>>

This report was generated on 2020-09-21 12:49:15 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> R version 4.0.2 (2020-06-22)
#> Platform: x86_64-pc-linux-gnu (64-bit)
#> Running under: Pop!_OS 20.04 LTS
#> 
#> Matrix products: default
#> BLAS:   /usr/lib/x86_64-linux-gnu/openblas-pthread/libblas.so.3
#> LAPACK: /usr/lib/x86_64-linux-gnu/openblas-pthread/liblapack.so.3
#> 
#> locale:
#>  [1] LC_CTYPE=en_US.UTF-8       LC_NUMERIC=C              
#>  [3] LC_TIME=en_US.UTF-8        LC_COLLATE=en_US.UTF-8    
#>  [5] LC_MONETARY=en_US.UTF-8    LC_MESSAGES=en_US.UTF-8   
#>  [7] LC_PAPER=en_US.UTF-8       LC_NAME=C                 
#>  [9] LC_ADDRESS=C               LC_TELEPHONE=C            
#> [11] LC_MEASUREMENT=en_US.UTF-8 LC_IDENTIFICATION=C       
#> 
#> attached base packages:
#> [1] splines   stats     graphics  grDevices utils     datasets  methods  
#> [8] base     
#> 
#> other attached packages:
#>  [1] scales_1.1.1              forcats_0.5.0            
#>  [3] stringr_1.4.0             dplyr_1.0.2              
#>  [5] purrr_0.3.4               readr_1.3.1              
#>  [7] tidyr_1.1.2               ggplot2_3.3.2            
#>  [9] tidyverse_1.3.0           lubridate_1.7.9          
#> [11] visreg_2.7.0              tibble_3.0.3             
#> [13] riskRegression_2020.02.05 prodlim_2019.11.13       
#> [15] flexsurv_1.1.1            survival_3.2-3           
#> [17] pracma_2.2.9              magrittr_1.5             
#> [19] kableExtra_1.2.1          glmnet_4.0-2             
#> [21] Matrix_1.2-18             data.table_1.13.0        
#> [23] cowplot_1.1.0             colorspace_1.4-1         
#> [25] casebase_0.9.0           
#> 
#> loaded via a namespace (and not attached):
#>  [1] TH.data_1.0-10      VGAM_1.1-3          ellipsis_0.3.1     
#>  [4] htmlTable_2.1.0     base64enc_0.1-3     fs_1.5.0           
#>  [7] rstudioapi_0.11     MatrixModels_0.4-1  fansi_0.4.1        
#> [10] mvtnorm_1.1-1       xml2_1.3.2          codetools_0.2-16   
#> [13] knitr_1.29          Formula_1.2-3       jsonlite_1.7.1     
#> [16] broom_0.7.0         cluster_2.1.0       dbplyr_1.4.4       
#> [19] png_0.1-7           compiler_4.0.2      httr_1.4.2         
#> [22] backports_1.1.9     assertthat_0.2.1    cli_2.0.2          
#> [25] htmltools_0.5.0     quantreg_5.67       tools_4.0.2        
#> [28] gtable_0.3.0        glue_1.4.2          Rcpp_1.0.5         
#> [31] cellranger_1.1.0    vctrs_0.3.4         nlme_3.1-149       
#> [34] conquer_1.0.2       iterators_1.0.12    xfun_0.17          
#> [37] rvest_0.3.6         lifecycle_0.2.0     polspline_1.1.19   
#> [40] muhaz_1.2.6.1       MASS_7.3-53         zoo_1.8-8          
#> [43] hms_0.5.3           sandwich_2.5-1      SparseM_1.78       
#> [46] RColorBrewer_1.1-2  rticles_0.15        yaml_2.2.1         
#> [49] gridExtra_2.3       rms_6.0-1           rpart_4.1-15       
#> [52] latticeExtra_0.6-29 stringi_1.5.3       foreach_1.5.0      
#> [55] checkmate_2.0.0     lava_1.6.7          shape_1.4.5        
#> [58] rlang_0.4.7         pkgconfig_2.0.3     matrixStats_0.56.0 
#> [61] evaluate_0.14       lattice_0.20-41     htmlwidgets_1.5.1  
#> [64] cmprsk_2.2-10       tidyselect_1.1.0    deSolve_1.28       
#> [67] R6_2.4.1            generics_0.0.2      Hmisc_4.4-1        
#> [70] multcomp_1.4-13     DBI_1.1.0           withr_2.2.0        
#> [73] pillar_1.4.6        haven_2.3.1         foreign_0.8-79     
#> [76] mgcv_1.8-33         nnet_7.3-14         mstate_0.2.12      
#> [79] modelr_0.1.8        crayon_1.3.4        rmarkdown_2.3      
#> [82] timereg_1.9.7       jpeg_0.1-8.1        grid_4.0.2         
#> [85] readxl_1.3.1        blob_1.2.1          reprex_0.3.0       
#> [88] digest_0.6.25       webshot_0.5.2       numDeriv_2016.8-1.1
#> [91] stats4_4.0.2        munsell_0.5.0       viridisLite_0.3.0  
#> [94] quadprog_1.5-8
\end{CodeOutput}
\end{CodeChunk}
